Loading and rsyncing a Data folder 
---

This package assumes that you have a separate folder containing project data.
It provides a function `rsync` to synchronize that folder with a remote folder, 
and a function `data.load` to load data from the project folder.

The data folder is assumed to be in an environment variable `R_DATA_ROOT`, defaulting to `~/data`

Installing
---

The package can be directly installed using `devtools`:

```{r message=F}
if (!require(devtools)) {install.packages("devtools"); library(devtools)}
install_github("vanatteveldt/datasync")
library(datasync)
```

Note: If `devtools` is not available, you can simple source the [data.r](R/data.r) file.

Loading and saving data
----

To demonstrate loading and saving data, let's setup a new folder in the temporary folder as data.folder

```{r}
set.data.folder(tempfile())
foo = "bar"
save.data(foo, file = "test.rdata")
rm("foo")
load.data("test.rdata")
foo
```

Obviously, there is not a lot of magic going on here. 
The use of these functions is to be able to set a data folder as an environment variable, 
so the project source code does not contain the reference to the local file system

Synchronizing data
----

The `rsync` function calls the rsync command as a system call to synchronize the data folder with a remote folder.

To demonstrate this function, I will use `localhost` as the "remote" host and synchronize with a second temporary folder:

```{r}
remote = tempfile()
dir.create(remote)
save(foo, file=file.path(remote, "test2.rdata"))
list.files(remote)
list.files(get.data.folder())
```

As you can see, the 'local' folder contains `test.rdata`, while the remote folder contains `test2.rdata`. 
To run the actual synchronization, call `rsync` with the remote host and remote folder, if it is different from the local folder:

```{r}
rsync(remote_host = "localhost", remote_folder = remote)
```

Let's inspect the folders:

```{r}
list.files(remote)
list.files(get.data.folder())
```

If we call rsync again, only new or changed files will synchronized. 
If a file is edited in both locations, the newer file will be kept. 
If a file is deleted in either location, it will be 'restored' from the other location.

<!--
library(knitr); knit("README.Rmd")
 -->